|

### 2021-10-06 appendix/appendix.Rmd
text edits, article and appendix
remove author information

---
title: |
       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
author:
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

@@

The expected utility for the city councilors depends on which reversal policy takes place. As mentioned above, we explore the implications of three different mechanisms. First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and the random selection of one councilor. The randomly selected councilor becomes the new proposer. If her proposal is accepted, it is implemented. If rejected, the budget shrinks again by $\delta$ and another city councilor is chosen to propose the policy. The process continues until the proposal is finally accepted.

>>>>

---
title: |
       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
author:
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

The expected utility for the city councilors depends on which reversal policy takes place. As mentioned above, we explore the implications of three different mechanisms. First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and the random selection of one councilor. The randomly selected councilor becomes the new proposer. If her proposal is accepted, it is implemented. If rejected, the budget shrinks again by $\delta$ and another city councilor is chosen to propose the policy. The process continues until a proposal is finally accepted.

### 2021-10-06 article/article.Rmd
remove author information

---
title:  |
        | Legislature Size and Welfare: Evidence from Brazil
author: 
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
date: \today
thanks: "We thank Cedric Antunes, Victor Araujo, Eric Arias, Taylor Boas, Natalia Bueno, Andrea Freitas, Saad Gulzar, James Mahon, Lucas Novaes, Nelson Ruiz, Catarina Roman, David Skarbek, and Denis Stukal for their valuable comments. We also thank the participants of seminars and conferences at CEPESP, CUNY, INSPER, IPSA, LACEA, LASA, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala. We gratefully acknowledge the financial support of the São Paulo Research Foundation (FAPESP), grant number 2017/07290-5. All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
abstract: "How does legislature size impact public service provision? Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood. In this paper, we use a formal model to show that increasing legislature size improves public goods provision. We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it. We test this theory by exploiting sharp discontinuities in city council size in Brazil. We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures. To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008. This paper has implications for the design of representative institutions."
abstractspacing: double
keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
jelcodes: H41; H80; I31; I38
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

>>>>

---
title:  |
        | Legislature Size and Welfare: Evidence from Brazil
author: 
date: \today
abstract: "How does legislature size impact public service provision? Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood. In this paper, we use a formal model to show that increasing legislature size improves public goods provision. We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it. We test this theory by exploiting sharp discontinuities in city council size in Brazil. We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures. To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008. This paper has implications for the design of representative institutions."
abstractspacing: double
keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
jelcodes: H41; H80; I31; I38
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@
